---
title: "Homework 1"
author: "Han Kim"
date: "01-29-2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
<br/><br/>

## Problem1

Use definitions to prove  
$\left(A^{-1}\right)^{T}$ = $\left(A^{T}\right)^{-1}$  
where A is an invertible square matrix and $A^{T}$ means the transpose of matrix A.

*** 

We know $(A*B)^{T}$ = $B^{T}*A^{T}$ and $A^{-1}$ \* $A$ = $E$.
So, $\left(A^{-1}*A\right)^{T}=A^{T}*\left(A^{-1}\right)^{T}=E^{T}=E$.<br>
Because $det(A^{T})$ is not zero, $\left(A^{T}\right)^{-1}*A^{T}*\left(A^{-1}\right)^{T}=\left(A^{-1}\right)^{T}=\left(A^{T}\right)^{-1}*E=\left(A^{T}\right)^{-1}$<br/><br/>

As a result, $\left(A^{-1}\right)^{T}=\left(A^{T}\right)^{-1}$


<br/><br/>

## Problem2
A bank makes four kinds of loans to its customers, and these loans yield the following annual interest rates to the bank:  

* First mortgage 14%  
* Second mortgage 20%  
* Home improvement 20%  
* Personal overdraft 10%  

We are interested in the bank’s lending strategy. The information we know is as following:  

1. In total $250 million is lent out.  
2. First mortgages are 55% of all mortgages (i.e., first and second mortgage) issued.  
3. Second mortgages are 25% of all loans issued.  
4. The average interest rate on all loans is 15%.  
Calculate the lending strategy using matrix inversion  

*** 

```{r}
A = matrix(c(1, 1, 1, 1, 
             0.45, -0.55, 0, 0, 
             0, 1, 0, 0, 
             0.14, 0.2, 0.2, 0.1), 4, 4, byrow = TRUE)
B = c(250, 0, 250*0.25, 250*0.15)

solve(A)%*%B

```

As a result, first morgage is \$76.38889 million, second mortage is \$62.5 million, home improvement is -\$79.16667 million and personal overdraft is \$154.17.  


<br/><br/>

## Problem3

A company manufactures four variants of the same product, and in the final part of the manufacturing process, there are assembly, polishing and packing operations. For each variant, the time required for these operations is shown below (in minutes) as is the profit per unit sold.

. | Assembly  | Polish  | Pack  | Profit($) 
---         | ---       | ---     |---    |---
Variant 1   | 2         | 3       | 2     | 1.50
2           | 4         | 2       | 3     | 2.50
3           | 3         | 3       | 2     | 3.00
4           | 7         | 4       | 5     | 4.50

Given the current state of the labor force the company estimate that they have 100000 minutes of assembly time, 50000 minutes of polishing time and 60000 minutes of packing time available. Add the non-negative constraints which ensure a positive number of units manufactured for each type of variant. Formulate this as a Linear Programming problem with appropriate decision variables, constraints, and an objective. Do not solve the program.


***

1. Decision variables
    + Variant1 = $x_{1}$
    + Variant2 = $x_{2}$
    + Variant3 = $x_{3}$
    + Variant4 = $x_{4}$

2. Coinstraints
    + $2x_{1}+4x_{2}+3x_{3}+7x_{4} \le 100000$
    + $3x_{1}+2x_{2}+3x_{3}+4x_{4} \le 50000$
    + $2x_{1}+3x_{2}+2x_{3}+5x_{4} \le 60000$
    + $x_{1}\ge 0$
    + $x_{2}\ge 0$
    + $x_{3}\ge 0$
    + $x_{4}\ge 0$

3. Objective function
    + $$\max_{x_{1},x_{2},x_{3},x_{4}} 1.5x_{1}+2.5x_{2}+3x_{3}+4.5x_{4}$$

<!-- ```{r} -->
<!-- library(lpSolve) -->
<!-- objective.in <- c(1.5, 2.5, 3, 4.5) -->
<!-- const.mat <- matrix(c(2, 4, 3, 7,  -->
<!--                       3, 2, 3, 4,  -->
<!--                       2, 3, 2, 5, -->
<!--                       1, 0, 0, 0, -->
<!--                       0, 1, 0, 0, -->
<!--                       0, 0, 1, 0, -->
<!--                       0, 0, 0, 1), nrow=7, byrow=TRUE) -->
<!-- const.rhs <- c(100000, 50000, 60000, 0, 0, 0, 0) -->
<!-- const.dir <- c("<=", "<=", "<=", ">=", ">=", ">=", ">=") -->
<!-- optimum <- lp(direction="max", objective.in, const.mat, const.dir, const.rhs) -->
<!-- optimum$solution -->
<!-- ``` -->


<br/><br/>

## Problem4

### Part a
Use “for loop(s)” and “if statement” within the loop to generate a 20 by 20 Lehmer matrix A where

$$A_{i,j}=\{_{\frac{j}{i},j<i}^{\frac{i}{j},j \ge i}$$

Hint: First generate a 4-by-4 matrix with all the elements being 0. Then use for loop(s) and if statement to
definite the Lehmer matrix. Find the 4-by-4 Lehmer matrix and use the Wikipedia to check. Then you can
change the code to run a 20 by 20

***

```{r}
library(MASS)

A = matrix(0, nrow = 20, ncol = 20)

for (i in 1:nrow(A)) {      # for loop of rows
  for (j in 1:ncol(A)) {    # for loop of columns
    if(j<i)
      A[i,j]=j/i
    else
      A[i,j]=i/j
  }
}

fractions(A) # Print matrix A as fractional numbers

```

<br/><br/>

### Part b


Test whether $A$ is symmetric or not. Namely, is $A$ equal to $A^{T}$?

***

```{r}

isSymmetric(A)
identical(A, t(A))

```

We can test whether $A$ is symmetric or not using 'isSymmetric' function. Also can check using 'identical' function between $A$ and $t(A)$.  
As a result, $A$ is symmetric.


<br/><br/>

### Part c

Calculate $C = A^{-1}$ in R. Test whether the inverse is correct. That is, calculate C × A in R and see whether the product is an identity matrix.  
Hint: Identity matrix can be generated using function $diag()$. You may use function $all.equal()$ to compare $C × A$ and the identity matrix

***

```{r}
C = solve(A) # Inverse matrix of A
fractions(C) # Print C as fractional numbers
I = diag(20) # Identity matrix with 20x20 dimension

all.equal(C%*%A,I) # Compare CXA and I

```

So, $C$ is inverse matrix of $A$.



<br/><br/>

### Part d

Assign [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1] to $d$ in R

Hint: This is a combination of sequence 1:10 and 10:1

***

```{r}
d <- c(1:10,10:1)
d

```



<br/><br/>

### Part e

Solve for x in the equation $Ax = Cd$

***

We konw that $C$ is inverse matrix of $A$($C=A^{-1}$). So $x = A^{-1}*C*d=C*C*d$.  

```{r}

x = C%*%C%*%d
fractions(x)    # Show solution as fractional numbers.

```

